Response to the defense feedback

### 2021-06-18 Chapter-6/Chapter-6.tex
Updates from Overleaf

\ctool{} can give a conservative estimation of the
side-channel leakage based on Channel Capacity. The channel capacity
measures the information flow between the source and the
destination. One useful characteristic of channel capacity is not
affected by the input, which is useful because we cannot
assume the input secrets of the software in practice. In Chapter~\ref{chapter5}, we
use the sampling result to approximate the true value of the
channel capacity. We prove the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.

>>>>

\ctool{} defines the amount of leaked information by the empirical entropy of the
observations. For a determinism program, channel capacity is the tight upper bound of the entropy of the observation. The quantification result is always smaller than the channel capacity and can approximate the value of the channel capacity in some cases. \ctool{} can give a conservative estimation of the
side-channel leakage based on Channel Capacity. The channel capacity
measures the information flow between the source and the
destination. One useful characteristic of channel capacity is not
affected by the input, which is useful because we cannot
assume the input secrets of the software in practice. In Chapter~\ref{chapter5}, we use the sampling result to approximate the true value of the
channel capacity. We show that the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.
